Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-11 final_metrics_analysis.Rmd

@@

>>>>

from aif360.algorithms.preprocessing import DisparateImpactRemover
from BlackBoxAuditing.repairers.GeneralRepairer import Repairer

@@

```{python pre-processing disparate impact remover}
#lr = LogisticRegressionCV(solver='lbfgs')
#rew = ReweighingMeta(estimator=lr, reweigher=Reweighing('race'))
#rew.fit(X_train, y_train)
#y_pred_REW = rew.predict(X_test)

diremover = DisparateImpactRemover(repair_level=1.0, sensitive_attribute="race")
#diremover.fit(X_train, y_train)
#y_pred_diremover = diremover.predict(X_test)

diremover_rp = diremover.fit_transform(X_test)
# AttributeError: 'DataFrame' object has no attribute 'features' (probem with .fit_transform function)
# .fit_transform() angry because of X_test...

```
